Concurrent Programming in Harmony

### 2021-02-08 book/paper.tex
Latest

Even though they are not strictly necessary, we encourage to include invariants
in your Harmony code. They can provide important insights into why the code works.

@@

Harmony can check these invariants as well.
$\mathcal{I}_2(i)$ is checked by the \texttt{assert} statement.
But how would one go about checking an
invariant like $\mathcal{I}_1$?  Invariants must hold for every state.
For $\mathcal{I}_2$ we only need an assertion at label \texttt{@cs} because the
premisse is that there is a thread at that label.  However, we would
like to check $\mathcal{I}_1$ in \emph{every state} (after the variables have
been initialized).
Harmony supports checking such invariants using the \texttt{invariant}
keyword.
The expression counts the number of \texttt{False} values and checks that
the result is less than or equal to 1.
Harmony checks the expression in every reachable state.

@@

First and foremost I would like to think my student Haobin Ni with
whom I've had numerous discussions about the design of Harmony.
Haobin even contributed some code to the Harmony compiler.

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Heather Zheng,
Lorenzo Alvisi,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.

>>>>

Even though they are not strictly necessary, we encourage you
to include invariants in your Harmony code.
They can provide important insights into why the code works.

@@

Harmony can check these invariants as well.
$\mathcal{I}_2(i)$ is checked by the \texttt{assert} statement.
But how would one go about checking an
invariant like $\mathcal{I}_1$?  Invariants must hold for every state.
For $\mathcal{I}_2$ we only need an assertion at label \texttt{@cs} because the
premise is that there is a thread at that label.  However, we would
like to check $\mathcal{I}_1$ in \emph{every state} (after the variables have
been initialized).
Harmony supports checking such invariants using the \texttt{invariant}
keyword.
The expression counts the number of \texttt{False} values and checks that
the result is less than or equal to 1.
Harmony checks the expression in every reachable state.

@@

First and foremost I would like to thank my student Haobin Ni with
whom I've had numerous discussions about the design of Harmony.
Haobin even contributed some code to the Harmony compiler.

@@

The following people contributed by making comments on or finding bugs in
early drafts of the book:
Alex Chang,
Anneke van Renesse,
Brendon Nguyen,
Hartek Sabharwal,
Heather Zheng,
Lorenzo Alvisi,
Saleh Hassen,
Sunwook Kim,
Trishita Tiwari,
Yidan Wang,
Zhuoyu Xu,
and
Zoltan Csaki.
